Leadership across cultures and contexts

### 2019-10-25 leadership_across_cultures_contexts.Rmd
Fixed errors on analyses script with repeated PCA analyses.
Adding CSV of SCCS and eRHAF (OWC) IDs.

Minor changes in Markdown file.

To reduce the dimensionality of the `r length(quality_vars)` quality variables and the

@@

The geographic distribution of the cultures in our sample is displayed in Fig. 1, with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The 1212 text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (89.8%, 898 text records) and very few pertained to female leadership (2.5%, 25 text records).In7 instances (0.7%)textrecordspertain tobothmales and females,and in69 text records (6.9%) sex was unknown.

>>>>

To reduce the dimensionality of the `r length(quality_vars)` quality variables and the `r length(function_vars)` we relied on logistic PCA from the Binary Dimensionality Reduction (logisticPCA) package CITE.

@@

The geographic distribution of the cultures in our sample is displayed in Fig. 1, with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture (for details, see Table S1). The 1212 text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, with a median word count of X, a mean of X, and standard deviation of X. The vast majority of text records pertained to male leadership (89.8%, 898 text records) and very few pertained to female leadership (2.5%, 25 text records). In 7 instances (0.7%)textrecordspertain tobothmales and females,and in 69 text records (6.9%) sex was unknown.
